% Chapter 1
\section*{\centering\fontsize{14}{16}\selectfont CHAPTER I}
\addcontentsline{toc}{section}{CHAPTER I}

% Introduction subsection
\subsection*{\centering\fontsize{12}{14}\selectfont INTRODUCTION}
\addcontentsline{toc}{subsection}{INTRODUCTION}

% Introduction: subsection
%\setstretch{1.5}
\subsubsection*{\fontsize{12}{14}\selectfont 1.1 Introduction}
\addcontentsline{toc}{subsubsection}{1.1 Introduction}

% Your content for the Introduction subsection goes here
\setstretch{1.5}
\fontsize{12}{14}\selectfont
In recent years, there has been a rise in the number of studies that investigate ways to transform wave energy into forms that can be used. This is an instant response to the rising interest in sustainable power and the many benefits connected with it, such as dependability, minimal carbon, and high density of power.\cite{ref1} This is a reaction to the increasing interest in sustainable energy and the numerous approval with it. This is a direct consequence of people's increasing interest in renewable sources of energy and the advantages that they provide. The process of converting wave energy into forms that may be put to use is currently in the preliminary phases of research and development.\cite{ref2,ref3,ref4} In the past ten years, a significant amount of time and effort has been invested in the academic research of WEC behavior and control. Since we originally began devoting how much time and effort into this endeavor, ten years have gone. From here, we move on to studying nonlinear hydrodynamics (especially nonlinear FK force), conducting CNWT simulations of wave energy converters \cite{ref3} and ultimately exploring nonlinear dynamics in general \cite{ref4}. When it comes to the process of developing appropriate controls, linear models are utilized rather frequently \cite{ref5}. Linear models are frequently utilized in the process of developing optimum control systems. Whilst also attempting to figure the most effective strategy to control a system, linear models are utilized rather frequently in many cases.\cite{ref6} During the past several years, there has been a considerable rise in the amount of research that is being done to investigate how the process of turning wave energy into useable forms might be made more cost-effective.

% Current situation of Renewable energy: subsection
\subsubsection*{\fontsize{12}{14}\selectfont 1.2 Current situation of Renewable energy}
\addcontentsline{toc}{subsubsection}{1.2 Current situation of Renewable energy}

% Your content for the Current situation of Renewable energy subsection goes here

% Project motivation: subsection
\subsubsection*{\fontsize{12}{14}\selectfont 1.3 Project motivation}
\addcontentsline{toc}{subsubsection}{1.3 Project motivation}

% Your content for the Project motivation subsection goes here

% Objectives: subsection
\subsubsection*{\fontsize{12}{14}\selectfont 1.4 Objectives}
\addcontentsline{toc}{subsubsection}{1.4 Objectives}

% Your content for the Objectives subsection goes here

% Problem description: subsection
\subsubsection*{\fontsize{12}{14}\selectfont 1.5 Problem description}
\addcontentsline{toc}{subsubsection}{1.5 Problem description}
\cite{ref7}
\cite{ref8}
\cite{ref9}
\cite{ref10}\cite{ref12}\cite{ref13}\cite{ref14}\cite{ref15}\cite{ref16}\cite{ref17}\cite{ref18}\cite{ref19}\cite{ref20}\cite{ref21}\cite{ref22}\cite{ref23}\cite{ref24}\cite{ref25}\cite{ref26}\cite{ref27}\cite{ref28}
% Your content for the Problem description subsection goes here
\clearpage

